### 2013-10-02 Rcode/intro.rmd
added small example of halfuniform in intro.rmd

So maybe it is the non-monotonic behaviour of the true beta values in this case.
Let's try putting in a component at -1.5 to make the data fit this assumption better:

@@

beta.ash=ash(betahat,s)
#compute the usual zscore and corresponding p value
zscore = betahat/s
pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
plot(qval$q,beta.ash$qval,main="comparison of ash and q value qvalues")
abline(a=0,b=1)

plot(cumsum(truenull[o])/(1:10000),qval$qval[o],col=2,type="l")
lines(cumsum(truenull[o])/(1:10000),beta.ash$qval[o])
abline(a=0,b=1)

>>>>

So maybe it is the non-monotonic behaviour of the true beta values in this case.
Let's try putting in a component at -1.5 to make the data fit this assumption better.

### Illustration of halfuniform method

I will also use this to illustrate the halfuniform method, which
allows for asymmetry.

@@

beta.ash=ash(betahat,s)
beta.ash.halfu = ash(betahat,s,"halfuniform")

hist(beta,prob=TRUE)
x = seq(-8,4,length=1000)
lines(x,density(beta.ash,x),col=2)
lines(x,density(beta.ash.halfu,x),col=3)

See how the use of the asymmtric uniform component does a better job capturing
the underlying density. Probably clearer in the cdf plot:
```{r}
plot(sort(beta),(1:length(beta))/length(beta),main="cdf of beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)
lines(x,cdf.ash(beta.ash.halfu,x),col=3,lwd=2)

#compute the usual zscore and corresponding p value
zscore = betahat/s
pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
plot(qval$q,beta.ash$qval,main="comparison of ash and q value qvalues")
abline(a=0,b=1)

o = order(qval$qval)
plot(cumsum(truenull[o])/(1:10000),qval$qval[o],col=1,type="l")
o = order(beta.ash$qval)
lines(cumsum(truenull[o])/(1:10000),beta.ash$qval[o],col=2)
o2 = order(beta.ash.halfu$qval)
lines(cumsum(truenull[o2])/(1:10000),beta.ash.halfu$qval[o2],col=3)

abline(a=0,b=1)
